\documentclass[a4paper]{article}
    \usepackage{hyperref}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=5in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.4in,right=0.4in,bottom=0.3in,top=0.5in]{geometry}
\usepackage{etoolbox,refcount}
\usepackage{multicol}


\newcounter{countitems}
\newcounter{nextitemizecount}
\newcommand{\setupcountitems}{%
  \stepcounter{nextitemizecount}%
  \setcounter{countitems}{0}%
  \preto\item{\stepcounter{countitems}}%
}
\makeatletter
\newcommand{\computecountitems}{%
  \edef\@currentlabel{\number\c@countitems}%
  \label{countitems@\number\numexpr\value{nextitemizecount}-1\relax}%
}
\newcommand{\nextitemizecount}{%
  \getrefnumber{countitems@\number\c@nextitemizecount}%
}
\newcommand{\previtemizecount}{%
  \getrefnumber{countitems@\number\numexpr\value{nextitemizecount}-1\relax}%
}
\makeatother    
\newenvironment{AutoMultiColItemize}{%
\ifnumcomp{\nextitemizecount}{>}{3}{\begin{multicols}{2}}{}%
\setupcountitems\begin{itemize}}%
{\end{itemize}%
\unskip\computecountitems\ifnumcomp{\previtemizecount}{>}{3}{\end{multicols}}{}}


    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.7ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%
\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,      
    urlcolor=black,
    pdftitle={Chitransh's Resume},
    pdfpagemode=FullScreen,
    }

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2 
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-9pt}
\begin{center}
	{\Huge \scshape {Chitransh Kulshrestha}}\\
	\vspace{2mm}
	India $\cdot$ chitransh.k2003@gmail.com $\cdot$ +91 6264234676 $\cdot$ \href{https://github.com/chitranshk1301}{GitHub} $\cdot$ \href{https://www.linkedin.com/in/chitransh-kulshrestha-00158a204//}{Linkedin} \\
\end{center}
\vspace{-1mm}
% \header{Objective}
% Dedicated, goal-oriented, and team-oriented individual who seeks an opportunity to work in the field of Web development\\
% \vspace{2mm}
%==== Education ====%
\header{Education}
\vspace{0mm}
\textbf{Indian Institute of Information Technology}\hfill Bhopal\\
BTech Information Technology \hfill December 2021 - Present\\
\vspace{1mm}
% \textbf{Relevant Coursework}
% \vspace{-2.5mm}
%  \begin{multicols}{2}
%     \begin{itemize}
%         \item Analysis of Algorithms
%          \vspace{-2.5mm}
%         \item Database Management System 
%          \vspace{-2.5mm}
%         \item Discrete Structures 
%          \vspace{-2.5mm}
%         \item Object Oriented Programming
%          \vspace{-2.5mm}
        
%     \end{itemize}
%     \end{multicols}
    
%     \vspace{-2mm}
    
\header{Professional Experience}

{\textbf{Stellarbyte }}\hfill August 2023 - October 2023 \\
 {\textit{Frontend development Intern }}  \
\vspace{-2.5mm}
\begin{itemize} 
\item Led end-to-end development of multiple projects using Reactjs, Nextjs and TailwindCSS, showcasing expertise in building efficient web applications from scratch.
\vspace{-2mm}
\item Created a comprehensive design system using Storybook, enhancing design consistency and accelerating project deployment, resulting in improved efficiency.
\item Optimized frontend for a chatbot with ChatGPT-like chat features using Styled Components and Tailwind CSS, delivering an engaging and visually appealing user interface.
\vspace{-2mm} 
\end{itemize}

{\textbf{HUBX }}\hfill July 2023 - August 2023 \\
 {\textit{Full stack web development Intern }}  \
\vspace{-2.5mm}
\begin{itemize} 
\item Developed and maintained a Next.js-based ecommerce platform, utilizing Prisma and Postgres for robust database management.
\vspace{-2mm}
\item Integrated a secure payment gateway, ensuring smooth and safe transaction processing.
\item Collaborated effectively with a cross-functional team, following Agile methodologies to deliver high-quality features on schedule.
\vspace{-2mm} 
\end{itemize}

{\textbf{Patilkaki }}\hfill December 2022 - January 2023 \\
 {\textit{Frontend development Intern }}  \
\vspace{-2.5mm}
\begin{itemize} 
\item Oversee front-end development using ReactJs to maintain application integrity with the backend and its efficiency.
\vspace{-2mm}
\item Utilize technologies such as Javascript, MaterialUI \& UIzard to
create UIs,
improved codebase quality and increased stability.
\vspace{-2mm}
\item Created pixel perfect frontend in ReactJs from the UIs. 
\end{itemize}
    
    \header{Projects}

{\textbf{Users Management}} \hfill
\vspace{-1mm}
% link to the project
\url{https://github.com/chitranshk1301/users-crud-mern}
\vspace{-1mm}
\begin{itemize} 
% 	add description for pet adoption system app.
    \item Developed a user management system with CRUD operations using MERN stack, enhanced with data visualization using Chart.js.
    \item Built a MERN-based solution for user management, featuring CRUD capabilities and data visualization through Chart.js.
    \item Implemented user management with MERN stack, enabling CRUD operations and integrating Chart.js for intuitive data representation.
    
\end{itemize}

{\textbf{Changelog-api}} \hfill
\vspace{-1mm}
% link to the project
\url{https://github.com/chitranshk1301/changelog-api}
\vspace{-1mm}
\begin{itemize} 
% 	add description for pet adoption system app.
    \item Created a \textbf{RESTful} API for logging different versions of your software.
    \item API includes CRUD operations on signin (with JWT auth), products and their updates.
    
\end{itemize}

{\textbf{PicNest}} \hfill
\vspace{-1mm}
% link to the project
\url{https://github.com/chitranshk1301/mern_image_crud}
\vspace{-1mm}
\begin{itemize}
    \item Developed a MERN project with secure user authentication, Cloudinary for image uploads, and a polished UI using Tailwind CSS. Users can create posts, and visibility is restricted to logged-in users.
    \vspace{-2mm}
    \item Built a simple and secure MERN app allowing users to upload and share images. Utilized Cloudinary for image management and enhanced the UI with Tailwind CSS.
\end{itemize}

{\textbf{ToDo's list using flask}} \hfill
\vspace{-1mm}
% link to the project
\url{https://github.com/chitranshk1301/todo-list-flask-based}
\vspace{-1mm}
\begin{itemize} 
% 	add description for pet adoption system app.
    \item Created todo's list (CRUD), frontend and backend, using flask (python based web framework) and SQL.
    \item Containerized it using \textbf{docker}.
    
\end{itemize}

% {\textbf{Pet adoption system}} \hfill
% \vspace{-1mm}
% % link to the project
% \url{http://pet-adoption-website.vercel.app/}
% \vspace{-1mm}
% \begin{itemize} 
% % 	add description for pet adoption system app.
%     \item Created a website for pet adoption using \textbf{ReactJs}.
%     \item Used an API to fetch information about pets available for adoption in a particular city.
    
% \end{itemize}

% {\textbf{Anime website}} \hfill
% \vspace{-1mm}
% % link to the project
% \url{http://anime-recommender-website.vercel.app/}
% \vspace{-1mm}
% \begin{itemize}
%     \item Created a website to search for an anime and animes related to it.
%     \vspace{-2mm}
%     \item Used a public API for anime data (\textbf{JIKAN API})
%     \item Created using \textbf{ReactJs and axios}
% \end{itemize}

    \header{Skills}
\vspace{2mm}
\begin{tabular}{ l l }
	Programming Languages: & C++ ,Python  \\
	\vspace{1mm}
	Tools:  & GitHub, Git, Latex, Postman \\
	Database Management Systems: & MySQL, PostgreSQL  \\ 
	Web Development:       & HTML , CSS (Bootstrap, Tailwind and Material UI) , JavaScript. Typescript   \\
	Libraries / Frameworks: & ReactJs , NodeJs , FastAPI, MongoDb, Prisma, ExpressJs        \\
	Soft Skills:           &  Leadership, Communication Skills, Organised , Quick learner  \\
	
\end{tabular}
\vspace{2mm}
 
 % \header{Position of Responsibility }
 % \vspace{0mm}

 % \textbf{GNU/Linux Users Club} \hfill IIIT Bhopal \\
 % \textit{Core team member} \hfill August 2022 - Present\\
 % \vspace{-2.5mm}
 % \begin{itemize} \itemsep 1pt
 % 	\item Using Arch Linux as my main distribution but I also have experienced most Debian Based( Ubuntu), Fedora and Arch based Distributions
 % 		\item Guiding batch mates to install and use Linux distributions comfortably as well as troubleshooting problems for them.
 % 		    \item Working as a \textbf{Web developer}.
 % \end{itemize}

\vspace{2mm}
\header{Achievements}
\textbf{Runner Up} \hfill GDSC IIIT Bhopal\\
Bagged second prize in Intra IIIT development contest conducted by GDSC IIIT Bhopal for creating a password manager.  
{\textit {Skills Used: Python, MySQl, Encryption Methods (MD5Sum)}}  \hfill 2022\\
\end{document}
